TRIK Studio: Technical Introduction

### 2017-03-09 2017-trikStudioEnglish/trikStudioEnglish.tex
translate reference list, fix figures caption syntax

\usepackage[font=small]{caption}
\captionsetup{singlelinecheck = false, justification=justified}
\usepackage{float}
\usepackage[colorlinks,filecolor=blue,citecolor=green,unicode,xetex]{hyperref}
\usepackage{cmap}
\usepackage{amsmath,amssymb}
\usepackage[mathcal]{euscript}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=1, pdfauthor=, pdfsubject=, pdfkeywords=}

@@

\section{Introduction}
\label{chapter:intro}
Current state of school education in computer science turned out quite like Seymour Papert predicted it to be. In 1967 he introduced a virtual Logo turtle, that is used to teach students programming at schools even nowadays. It is less known that Papert also used a mechanical robot turtle in his experiments, that was controlled from a computer~\cite{papert1980mindstorms}, and that made educational process much more entertaining. Today Papert's ideas are widely spread, a lot of schools are using robots to teach programming (for instance, in Russia robotics is a part of compulsory education program within the Technology course~\cite{лучин2016внедрение}). Several robotics educational kits are used, including Lego Mindstorms NXT, Lego Mindstorms EV3\footnote{LEGO Mindstorms homepage, URL: http://www.lego.com/en-us/mindstorms (accessed: 07.02.2017)}, TRIK\footnote{TRIK robotics platform homepage, URL: http://www.trikset.com/ (accessed: 07.02.2017)} etc.

@@

One of the most interesting and demanded TRIK Studio features is generation of well-readable textual code from visual diagrams. Several languages are supported for code generation: C, JavaScript, F\#, Pascal, Russian version of C~\cite{тереховотечественные} and byte code for Lego EV3 virtual machine. This section presents only code generators for control-flow programs.

@@

The second task is solved by a control flow analyzer module. In terms of a textual language the task is rephrased like this: by a given program containing \texttt{goto} statements create an equivalent structured program. This problem was solved by researchers in the code decompilation field~(\cite{steven1997advanced,деревенец2009структурный}). For example, such an algorithm based on interval analysis of control flow graph is presented in~\cite{steven1997advanced}. With minor modifications it was implemented in TRIK Studio. It is briefly described below.

@@

The described language has proven to be quite effective at specifying spatial and temporal constraints on a system state. It is more expressive than, for example, temporal logic or topological temporal logic languages which are used for specification of formal constraints on robot behavior in recent works~(\cite{mordvinov2016formal,kress2007s,бугайченко2007разработка,дмитриев2013адаптация}). The constraints checking system is also used for functional testing of TRIK Studio on continuous integration server. For more information on this (and other details of TRIK Studio testing) see in~\cite{mordvinov2016testing}.

>>>>

\usepackage[font=small]{caption}
\captionsetup{singlelinecheck = false, justification=justified, labelsep=period}
\usepackage{float}
\usepackage[colorlinks,filecolor=blue,citecolor=green,unicode,xetex]{hyperref}
\usepackage{cmap}
\usepackage{amsmath,amssymb}
\usepackage[mathcal]{euscript}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=1, pdfauthor=, pdfsubject=, pdfkeywords=}

@@

\section{Introduction}
\label{chapter:intro}
Current state of school education in computer science turned out quite like Seymour Papert predicted it to be. In 1967 he introduced a virtual Logo turtle, that is used to teach students programming at schools even nowadays. It is less known that Papert also used a mechanical robot turtle in his experiments, that was controlled from a computer~\cite{papert1980mindstorms}, and that made educational process much more entertaining. Today Papert's ideas are widely spread, a lot of schools are using robots to teach programming (for instance, in Russia robotics is a part of compulsory education program within the Technology course~\cite{luchin2016intro}). Several robotics educational kits are used, including Lego Mindstorms NXT, Lego Mindstorms EV3\footnote{LEGO Mindstorms homepage, URL: http://www.lego.com/en-us/mindstorms (accessed: 07.02.2017)}, TRIK\footnote{TRIK robotics platform homepage, URL: http://www.trikset.com/ (accessed: 07.02.2017)} etc.

@@

One of the most interesting and demanded TRIK Studio features is generation of well-readable textual code from visual diagrams. Several languages are supported for code generation: C, JavaScript, F\#, Pascal, Russian version of C~\cite{terekhovTools} and byte code for Lego EV3 virtual machine. This section presents only code generators for control-flow programs.

@@

The second task is solved by a control flow analyzer module. In terms of a textual language the task is rephrased like this: by a given program containing \texttt{goto} statements create an equivalent structured program. This problem was solved by researchers in the code decompilation field~(\cite{steven1997advanced,derevenets2009structural}). For example, such an algorithm based on interval analysis of control flow graph is presented in~\cite{steven1997advanced}. With minor modifications it was implemented in TRIK Studio. It is briefly described below.

@@

The described language has proven to be quite effective at specifying spatial and temporal constraints on a system state. It is more expressive than, for example, temporal logic or topological temporal logic languages which are used for specification of formal constraints on robot behavior in recent works~(\cite{mordvinov2016formal,kress2007s,bugaichenko2007development,dmitriev2013adaptation}). The constraints checking system is also used for functional testing of TRIK Studio on continuous integration server. For more information on this (and other details of TRIK Studio testing) see in~\cite{mordvinov2016testing}.
